AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-03 article/tex/main.tex
polishes conclusions and future work

\section{Conclusions and future work}
We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico.
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively with curiosity and open-minded as well as to develop a sense of wonder and joy in learning.

As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.

@@

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Rocio Montenegro for her contributions and input as Montessori teacher. 
To Elva Corona for her contributions on giving vision to the goals of the project. 
To Marta P\'erez, Donato Badillo-Per\'ez and Antonio Badillo-Per\'e\ for their interest as initial testers of the project. 
To Leticia Vazques for her inputs as a teacher of teenagers. 
To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
To Dago Cruz for his contributions on open source AI and Robotics.
To all of you of whom with the limited time were able to contribute to this work to make it more solid.
Thanks to Miguel Xochicale to orchestrate this project.
\end{acks}

>>>>

\section{Conclusions and future work}
In this work, we coin the term AIR4Children as a project that aims to tackle aspects of inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico.
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively, with curiosity and open-minded as well as to develop a sense of wonder and joy for learning.

As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children and to the community.

@@

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Rocio Montenegro for her contributions and input as Montessori teacher. 
To Elva Corona for her contributions on giving vision to the goals of the project. 
To Marta P\'erez, Donato Badillo-Per\'ez and Antonio Badillo-Per\'e\ for their interest as initial testers of the project. 
To Leticia Vazques for her inputs as a teacher of teenagers. 
To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
To Dago Cruz for his contributions on open source AI and Robotics.
To all of you of whom with the limited time were able to contribute to this work to make a bit more solid.
Thanks to Miguel Xochicale to orchestrate AIR4Children.
\end{acks}
